Analysis with nested effects

### 2017-04-21 Analysis.Rmd
Rearrange nested analysis
Nest REP within WMGT

Remove Analysis.Rmd and move Analysis_nested_effects.Rmd to Analysis.Rmd

Add R session info to analysis document

Rotate facet ribbon text, names no longer need to be changed/shortened

@@

eprior <- list(R = list(V = 1, nu = 0.02),
               G = list(G1 = list(V = 1, nu = 0.02, alpha.V = 1000)))
LShB_lmm_2015 <- MCMCglmm(LShB_AUDPS ~ WMGT * NRTE,
                          random = ~REP, 
                          data = as.data.frame(AUDPS_2015),
                          verbose = FALSE,
                          prior = eprior,
                          nitt = 5e+05,
                          burnin = 5000,
                          thin = 100,
                          pr = TRUE)

@@

# create data frames for generating diagnostic plots
reps <- data.frame(LShB_lmm_2015$Sol[, c(1, 7:10)])
x <- 1:nrow(reps)
reps <- melt(reps)

trts <-  data.frame(LShB_lmm_2015$Sol[, 2:6])
names(trts)[names(trts) == "WMGTFLD.NRTE100"] <- "FLD.NRTE100"
names(trts)[names(trts) == "WMGTFLD.NRTE120"] <- "FLD.NRTE120"
trts <- melt(trts)

@@

eprior <- list(R = list(V = 1, nu = 0.02),
               G = list(G1 = list(V = 1, nu = 0.02, alpha.V = 1000)))
TShB_severity_lmm_2015 <- MCMCglmm(TShB_AUDPS ~ WMGT * NRTE,
                                   random = ~REP, 
                          data = as.data.frame(AUDPS_2015),
                          verbose = FALSE,
                          prior = eprior,
                          nitt = 5e+05,
                          burnin = 5000,
                          thin = 100,
                          pr = TRUE)

@@

# create data frames for generating diagnostic plots
reps <- data.frame(TShB_severity_lmm_2015$Sol[, c(1, 7:10)])
reps <- melt(reps)

trts <-  data.frame(TShB_severity_lmm_2015$Sol[, 2:6])
names(trts)[names(trts) == "WMGTFLD.NRTE100"] <- "FLD.NRTE100"
names(trts)[names(trts) == "WMGTFLD.NRTE120"] <- "FLD.NRTE120"
trts <- melt(trts)

@@

eprior <- list(R = list(V = 1, nu = 0.02),
               G = list(G1 = list(V = 1, nu = 0.02, alpha.V = 1000)))
TShB_incidence_lmm_2015 <- MCMCglmm(TShB_incidence_mean ~ WMGT * NRTE,
                                    random = ~REP, 
                          data = as.data.frame(AUDPS_2015),
                          verbose = FALSE,
                          prior = eprior,
                          nitt = 5e+05,
                          burnin = 5000,
                          thin = 100,
                          pr = TRUE)

@@

# create data frames for generating diagnostic plots
reps <- data.frame(TShB_incidence_lmm_2015$Sol[, c(1, 7:10)])
reps <- melt(reps)

trts <-  data.frame(TShB_incidence_lmm_2015$Sol[, 2:6])
names(trts)[names(trts) == "WMGTFLD.NRTE100"] <- "FLD.NRTE100"
names(trts)[names(trts) == "WMGTFLD.NRTE120"] <- "FLD.NRTE120"
trts <- melt(trts)

@@

eprior <- list(R = list(V = 1, nu = 0.02),
               G = list(G1 = list(V = 1, nu = 0.02, alpha.V = 1000)))
LShB_lmm_2016 <- MCMCglmm(LShB_AUDPS ~ WMGT * NRTE,
                          random = ~REP, 
                          data = as.data.frame(AUDPS_2016),
                          verbose = FALSE,
                          nitt = 5e+05,
                          burnin = 5000,
                          thin = 100,
                          prior = eprior,
                          pr = TRUE)

@@

# create data frames for generating diagnostic plots
reps <- data.frame(LShB_lmm_2016$Sol[, c(1, 5:8)])
reps <- melt(reps)

trts <-  data.frame(LShB_lmm_2016$Sol[, 2:4])
names(trts)[names(trts) == "WMGTFLD.NRTE180"] <- "FLD.NRTE180"
trts <- melt(trts)

@@

eprior <- list(R = list(V = 1, nu = 0.02),
               G = list(G1 = list(V = 1, nu = 0.02, alpha.V = 1000)))
TShB_severity_lmm_2016 <- MCMCglmm(TShB_AUDPS ~ WMGT * NRTE,
                                   random = ~REP, 
                          data = as.data.frame(AUDPS_2016),
                          verbose = FALSE,
                          nitt = 5e+05,
                          burnin = 5000,
                          thin = 100,
                          prior = eprior,
                          pr = TRUE)

@@

# create data frames for generating diagnostic plots
reps <- data.frame(TShB_severity_lmm_2016$Sol[, c(1, 5:8)])
reps <- melt(reps)

trts <-  data.frame(TShB_severity_lmm_2016$Sol[, 2:4])
names(trts)[names(trts) == "WMGTFLD.NRTE180"] <- "FLD.NRTE180"
trts <- melt(trts)

@@

eprior <- list(R = list(V = 1, nu = 0.02),
               G = list(G1 = list(V = 1, nu = 0.02, alpha.V = 1000)))
TShB_incidence_lmm_2016 <- MCMCglmm(TShB_incidence_mean ~ WMGT * NRTE, 
                                    random = ~REP, 
                          data = as.data.frame(AUDPS_2016),
                          verbose = FALSE,
                          prior = eprior,
                          nitt = 5e+05,
                          burnin = 5000,
                          thin = 100,
                          pr = TRUE)

@@

# create data frames for generating diagnostic plots
reps <- data.frame(TShB_incidence_lmm_2016$Sol[, c(1, 5:8)])
reps <- melt(reps)

trts <-  data.frame(TShB_incidence_lmm_2016$Sol[, 2:4])
names(trts)[names(trts) == "WMGTFLD.NRTE100"] <- "FLD.NRTE100"
names(trts)[names(trts) == "WMGTFLD.NRTE120"] <- "FLD.NRTE120"
trts <- melt(trts)

@@

The models all appear to be good fits after increasing the number of iterations.
None of the treatments in either year, 2015 or 2016, were significant. The
see `pMCMC` values and also posterior graphs. There is a large amount of overlap
in all of the posterior graphs.

>>>>

## Setup
Use set seed for reproducibility.

```{r set_seed}
set.seed(27)
```

@@

eprior <- list(R = list(V = 1, nu = 0.02),
               G = list(G1 = list(V = 1, nu = 0.02, alpha.V = 1000)))
LShB_lmm_2015 <- MCMCglmm(LShB_AUDPS ~ WMGT * NRTE,
                          random = ~WMGT:REP, 
                          data = as.data.frame(AUDPS_2015),
                          verbose = FALSE,
                          prior = eprior,
                          nitt = 5e+05,
                          burnin = 5000,
                          thin = 100,
                          pr = TRUE)

@@

# create data frames for generating diagnostic plots
reps <- data.frame(LShB_lmm_2015$Sol[, c(1, 7:14)])
x <- 1:nrow(reps)
reps <- melt(reps)

trts <-  data.frame(LShB_lmm_2015$Sol[, 2:6])
trts <- melt(trts)

@@

eprior <- list(R = list(V = 1, nu = 0.02),
               G = list(G1 = list(V = 1, nu = 0.02, alpha.V = 1000)))
TShB_severity_lmm_2015 <- MCMCglmm(TShB_AUDPS ~ WMGT * NRTE,
                                   random = ~WMGT:REP, 
                          data = as.data.frame(AUDPS_2015),
                          verbose = FALSE,
                          prior = eprior,
                          nitt = 5e+05,
                          burnin = 5000,
                          thin = 100,
                          pr = TRUE)

@@

# create data frames for generating diagnostic plots
reps <- data.frame(TShB_severity_lmm_2015$Sol[, c(1, 7:14)])
reps <- melt(reps)

trts <-  data.frame(TShB_severity_lmm_2015$Sol[, 2:6])
trts <- melt(trts)

@@

eprior <- list(R = list(V = 1, nu = 0.02),
               G = list(G1 = list(V = 1, nu = 0.02, alpha.V = 1000)))
TShB_incidence_lmm_2015 <- MCMCglmm(TShB_incidence_mean ~ WMGT * NRTE,
                                    random = ~WMGT:REP, 
                          data = as.data.frame(AUDPS_2015),
                          verbose = FALSE,
                          prior = eprior,
                          nitt = 5e+05,
                          burnin = 5000,
                          thin = 100,
                          pr = TRUE)

@@

# create data frames for generating diagnostic plots
reps <- data.frame(TShB_incidence_lmm_2015$Sol[, c(1, 7:14)])
reps <- melt(reps)

trts <-  data.frame(TShB_incidence_lmm_2015$Sol[, 2:6])
trts <- melt(trts)

@@

eprior <- list(R = list(V = 1, nu = 0.02),
               G = list(G1 = list(V = 1, nu = 0.02, alpha.V = 1000)))
LShB_lmm_2016 <- MCMCglmm(LShB_AUDPS ~ WMGT * NRTE,
                          random = ~WMGT:REP, 
                          data = as.data.frame(AUDPS_2016),
                          verbose = FALSE,
                          nitt = 5e+05,
                          burnin = 5000,
                          thin = 100,
                          prior = eprior,
                          pr = TRUE)

@@

# create data frames for generating diagnostic plots
reps <- data.frame(LShB_lmm_2016$Sol[, c(1, 5:12)])
reps <- melt(reps)

trts <-  data.frame(LShB_lmm_2016$Sol[, 2:4])
trts <- melt(trts)

@@

eprior <- list(R = list(V = 1, nu = 0.02),
               G = list(G1 = list(V = 1, nu = 0.02, alpha.V = 1000)))
TShB_severity_lmm_2016 <- MCMCglmm(TShB_AUDPS ~ WMGT * NRTE,
                                   random = ~WMGT:REP, 
                          data = as.data.frame(AUDPS_2016),
                          verbose = FALSE,
                          nitt = 5e+05,
                          burnin = 5000,
                          thin = 100,
                          prior = eprior,
                          pr = TRUE)

@@

# create data frames for generating diagnostic plots
reps <- data.frame(TShB_severity_lmm_2016$Sol[, c(1, 5:12)])
reps <- melt(reps)

trts <-  data.frame(TShB_severity_lmm_2016$Sol[, 2:4])
trts <- melt(trts)

@@

eprior <- list(R = list(V = 1, nu = 0.02),
               G = list(G1 = list(V = 1, nu = 0.02, alpha.V = 1000)))
TShB_incidence_lmm_2016 <- MCMCglmm(TShB_incidence_mean ~ WMGT * NRTE, 
                                    random = ~WMGT:REP, 
                          data = as.data.frame(AUDPS_2016),
                          verbose = FALSE,
                          prior = eprior,
                          nitt = 5e+05,
                          burnin = 5000,
                          thin = 100,
                          pr = TRUE)

@@

# create data frames for generating diagnostic plots
reps <- data.frame(TShB_incidence_lmm_2016$Sol[, c(1, 5:12)])
reps <- melt(reps)

trts <-  data.frame(TShB_incidence_lmm_2016$Sol[, 2:4])
trts <- melt(trts)

@@

The models all appear to be good fits.

None of the diagnostic plots show any signs of autocorrelation or any other obvious patterns.

None of the treatments in either year, 2015 or 2016, were significant. The
see `pMCMC` values and also posterior graphs. There is a large amount of overlap
in all of the posterior graphs.

The random effects all appear to be acceptable, the dotted line stays near to the solid line with no discernable patterns.

The random effects are all fairly equally distributed except for 2016 tiller sheath blight severity where water management:replicate has a larger effect. This is not surprising given that the plot and replicate sizes were different in 2016 due to the use of two fields in the IRRI experiment station, see the [2016 plot layout plan](https://github.com/adamhsparks/AWD_ShB_Interaction/blob/master/doc/Metadata/2016%20AWD%20ShB%20Metadata/ExptLayoutAWD2016.pdf).

# R Session Info
```{r session_info}
sessionInfo()
```
